Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
figuretweak
figure placement
Extremely important change...

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~K.~Ness\altaffilmark{4},
        Hans-Walter~Rix\altaffilmark{4},
    and~Daniel~Foreman-Mackey\altaffilmark{6}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th Floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Phyics,
  New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195-1580}
\email{david.hogg@nyu.edu}

@@

\begin{figure}[!p]
\includegraphics[width=2\figwidth]{./figs/clusters_0256.png}
\caption{The distribution of membership and density for the 256
  abundance-space clusters returned by the k-means algorithm at
  $K=256$.  The densest cluster (which is displayed in more detail in 
  \figurename~\ref{fig:M13}) is far more dense than the second
  densest.\label{fig:densities}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0253}
\caption{Same as \figurename~\ref{fig:all} except that the entire
  sample has been made gray and the members of the most dense
  $K=256$ abundance-space clusters have been rendered as unique, prominent triangles.
  This cluster, which was identified only in abundance space (six
  projections of which are the top six panels in this \figurename),
  turns out to be dominated by the halo globular cluster
  M13.\label{fig:M13}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0034}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the disrupting globular
  cluster Palomar 5.\label{fig:Pal5}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0177}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the Sagittarius star
  cloud.\label{fig:Sgr}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0010}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a high-velocity-dispersion
  structure in the Galaxy halo.\label{fig:halo}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0141}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a very thin young stellar
  structure in the Galaxy disk.\label{fig:disk}}
\end{figure}

>>>>

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~K.~Ness\altaffilmark{4},
        Hans-Walter~Rix\altaffilmark{4},
    and~Daniel~Foreman-Mackey\altaffilmark{6,7}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th Floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Phyics,
  New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Sagan Fellow}
\altaffiltext{7}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195-1580}
\email{david.hogg@nyu.edu}

@@

\begin{figure}[!bp]
\includegraphics[width=1.5\figwidth]{./figs/clusters_0256.png}
\caption{The distribution of membership and density for the 256
  abundance-space clusters returned by the k-means algorithm at
  $K=256$.  The densest cluster (which is displayed in more detail in 
  \figurename~\ref{fig:M13}) is far more dense than the second
  densest.\label{fig:densities}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0253}
\caption{Same as \figurename~\ref{fig:all} except that the entire
  sample has been made gray and the members of the most dense
  $K=256$ abundance-space clusters have been rendered as unique, prominent triangles.
  This cluster, which was identified only in abundance space (six
  projections of which are the top six panels in this \figurename),
  turns out to be dominated by the halo globular cluster
  M13.\label{fig:M13}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0034}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the disrupting globular
  cluster Palomar 5.\label{fig:Pal5}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0177}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the Sagittarius star
  cloud.\label{fig:Sgr}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0010}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a high-velocity-dispersion
  structure in the Galaxy halo.\label{fig:halo}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0141}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a very thin young stellar
  structure in the Galaxy disk.\label{fig:disk}}
\end{figure}
